Results

### 2021-10-25 Manuscript/Manuscript.Rmd
update

---
title: "Manuscript"
author: "Angelo D'Ambrosio"
date: "12/1/2021"
output:
  github_document
---

```{r Setup, include=FALSE}

knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))

knitr::opts_chunk$set(
	echo = FALSE,
	error = FALSE,
	message = T,
	warning = FALSE,
	dpi = 400
)

source('Setup.R')

if (!file.exists('annotation_summary.rds')) {
	annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)

	saveRDS(annotation_summary, 'annotation_summary.rds')
} else annotation_summary <- readRDS('annotation_summary.rds')

@@

## Results

```{r Results}

summary_table <- bind_rows(
    annotation_summary %>%  filter(Ord == 1) %>% mutate(Ord = 0, File = 'Input_P_R', Value = replace(Value, !str_detect(Label, 'Reviewed'), 0)),
    annotation_summary 
) %>% 
    filter(Label != 'Discordant') %>% 
    mutate(
        Task = case_when(str_detect(File, 'P_R') ~ 'R', T ~ 'P'),
        Ord = Ord + 1
    ) %>% 
    select(Ord, Value, Total_records, Label, Task, Batch) %>% 
    tidyr::pivot_wider(names_from = Label, values_from = Value) %>% 
    transmute(
        Task = Ord,
        Task_type = .$Task,
        across(c(Reviewed_positive, Reviewed_negative), ~ sapply(Task, function(i) {
            ret = ''
            if (Task_type[i] == 'R' & i != 1) {
                prev.i <- max(Task[Task < i])

                diff <- .x[i] - .x[prev.i]

                if (diff != 0) ret <- paste0(' ', ifelse(diff > 0, '+', ''), diff)
            }
            ret
        }), .names = "new_{.col}"),
        Uncertain = ifelse(
            Task_type == 'R',
            '',
            sprintf('%d (%s)%s', Uncertain, percent(Uncertain/Total_records), ifelse(New_uncertain > 0 , paste0(' +', New_uncertain), ''))
        ),
        Positive = ifelse(
            Task_type == 'R',
            sprintf('%d (%s)%s', Reviewed_positive, percent(Reviewed_positive/Total_records), new_Reviewed_positive),
            sprintf('%d (%s)%s', Positive, percent(Positive/Total_records), ifelse(New_positive > 0, paste0(' +', New_positive), ''))
        ),
        Negative = ifelse(
            Task_type == 'R',
            sprintf('%d (%s)%s', Reviewed_negative, percent(Reviewed_negative/Total_records), new_Reviewed_negative),
            sprintf('%d (%s)', Negative, percent(Negative/Total_records))
        ),
        Reviewed = ifelse(Task_type == 'R', Reviewed, ''),
        Batch = factor(Batch) %>% as.numeric(),
        New_rev_pos = NULL
    ) %>% select(-matches('new')) %>% rename(`Task type` = Task_type) %>% group_split(Batch) %>% lapply(function(df) select(df, -Batch))
```

### First search session

```{r Result 1}

first_batch <- "Records_2020-12-11"

first_query_file <- file.path("Annotations", first_batch, "Records_11.12.20.xlsx")

sources_first_query <- summarise_by_source(first_query_file) %>% as.list()

first_annotation_results <- annotation_summary %>%
	filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
		df <- .
		df$Value %>% setNames(df$Label) %>% as.list()
	}

new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum()

new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum()

all_unique_reviews <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed') %>% pull(Value) %>% max()

task_table <- summary_table[[1]]$`Task type` %>% table()

final_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'Reviewed_positive') %>% pull(Value) %>% max()
```

The first session of searches, performed using the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results for Pubmed, `r sources_first_query$WOS` for Web of Science, and `r sources_first_query$IEEE` for IEEE.\
Of these records, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review. Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.

Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is then used to reclassify all records (P tasks). After task 11, two susbsequent P tasks returned no uncertain or positive unreviewed predictions, therefore the first session was termined. In total `r task_table[['R']] - 1` review tasks were required in addition to the initial manual classification (tab. 1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive).\
Overall `r new_uncertains + new_positives + first_annotation_results$Reviewed` classification/review actions on `r all_unique_reviews` records were required, that is the `r percent((new_uncertains + new_positives + first_annotation_results$Reviewed)/sources_first_query$Total)` of the total number of records (`r sources_first_query$Total`) collected in the first session, while the rest was classified automatically as non-relevant.
The dataset at the end of the session contained a total of `r final_positives` positive records (+`r final_positives - first_annotation_results$Reviewed_positive` positive records compared to the initial manual classification).

`r knitr::kable(summary_table[[1]], caption = 'Table 1. Prediction (P) / review (R) tasks\' results after the first query was performed. The Uncertain column shows the number of new labeled records not already reviewed in the precedent tasks and the possible increment compared to the previous P task. The Positive column has different meaning for the type of task: for the P tasks is the number of positevely labeled records followed by the number of new positives not previously reviewed, if any; for the R task, the cumulative number of positive and its increment, if any. The same interpretation stands for the Negative column, albeit increments are not shown for the R tasks, since the negative predictions are not reviewed. All values are also shown as percentege over total of records available in the session.')`

### Second search session

>>>>

---
title: Main manuscript
authors:
  - name: David S. Hippocampus
    thanks: Use footnote for providing further information about author (webpage, alternative address)---*not* for acknowledging funding agencies. Optional.
    department: Department of Computer Science
    affiliation: Cranberry-Lemon University
    location: Pittsburgh, PA 15213
    email: hippo@cs.cranberry-lemon.edu
  - name: Elias D. Striatum
    department: Department of Electrical Engineering
    affiliation: Mount-Sheikh University
    location: Santa Narimana, Levand
    email: stariate@ee.mount-sheikh.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - blah
  - blee
  - bloo
  - these are optional and can be removed
bibliography: references.bib
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

```{r, echo=FALSE, results='asis', message = FALSE, warning = FALSE, error = FALSE, dpi = 400, fig.width=12, fig.height=5}

getOption("mc.cores", parallel::detectCores())

out <- unlist(lapply(c(
	'Manuscript_Introduction.Rmd',
	'Manuscript_Methods.Rmd',
	'Manuscript_Results.Rmd',
	'Manuscript_Discussion.Rmd'
), knitr::knit_child, quiet = TRUE))

cat(out, sep = '\n')

@@

\newpage

# References

### 2021-10-25 Manuscript/Manuscript_Discussion.Rmd
update

## Discussion

We propose a new integrated framework to help researcher collect and screen research publications characterized by high performance and versatility, joining the growing field of systematic review automatization (SRA) and helpers (SRH) tools.\
The International Collaboration for the Automation of Systematic Reviews (ICASR) proposes a number of features tools for automatic research synthesis should possess, defining the so called Vienna Principles [@beller2018making].We tried to adopt some of the concepts advocated by the ICAS; for example we are sharing the tool as an open source R package, and we tried to follow the paradigms of modular programming [@mccracken2003modular], building separated components communicating through intermediate outputs stored in common formats (Comma Separated Values/Microsoft Excel™), which make it possible for users to extend the framework or integrate it with other tools in their pipeline.\
Our framework has two main components, an integrated query-based citation search and management engine and an active machine learning record screener\

Our search engine is capable of automatically collecting citation data from three well known scientific databases, that is, Pubmed, Web of Science and the database of the Institute of Electrical and Electronics Engineers, implementing also institutional access rights; in addition, it can process manually downloaded results from all mentioned databases plus records from the SCOPUS and EMBASE databases. Once the citations are downloaded, they are translated in a uniform format and deduplicated. The online search algorithm is efficient enough to manage tens of thousands of search results, using various expedients to overcome the online databases limitations in terms of traffic and download quota. Most SRH tools we are aware of, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/), often focused on a particular topic [@visser2010performing] or relying on only one external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia]. To our knowledge, our tool is the first capable to fully automatize searching on three different well known scientific databases and to import raw data from five of them. Mixing different database is fundamental to have a more complete view of the literature on a topic [@bajpai2011search; @wilkins2005embase; @woods1998medline]: in our results, 18.7% of the positive matches were unique for one of the different data sources and no positive record was present among all of them (data not shown).\

Modern NLP techniques were used to transform textual data into actionable numeric inputs [@ananiadou2006text; @cohen2008getting]. One particular improvement was to use network analysis to identify associated terms, which we labelled as non-consecutive ngrams, which confer particular meaning when present together into a text while not necessary being close to each other. A similar network approach was used to merge redundant terms, in order to make model estimation more efficient and reduce possible noise. The use of network inspired modeling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text] and is a valuable tool to extract semantic information not evident in one-word of consecutive ngram models.

The citation screening functionality of the framework implements active machine learning based document classification, adopting best practices and bringing further improvements at various levels. At the base of our classification algorithm we use BART [@chipman2010bart; @kapelner2013bartmachine], a Bayesian machine learning technique characterized by exceptional predictive performance and speed even in large dataset. This model builds consecutive decision trees associating the presence/absence of set of terms to the probability of a positive match, each tree trying to decrease the prediction error of the precedent one [@hastie2009boosting]. The Bayesian approach explore distributions of trees which are justified by the data, while using a set of prior distributions to avoid overfitting by discouraging excessively deep trees, long sequences of trees, or extreme predicted probabilities. To further improve generalizability we ran multiple replications of the model and then averaged their record predictive distributions; this technique is called ensembling and it has been shown to improve out-of-sample predictive performance []. In a Bayesian setting, this effect comes from a reduction of the probability mass in the tails of the predictive distributions while not shifting their locations (i.e., it decreases variance without impacting bias) [bias/variance tradeoff, better if in Bayesian analysis and/or focusing to ensemble]. Instead, imposing stronger general priors against extreme predictions would decreased variance but also shifted the distribution mass towards a non-decision zone, therefore increasing bias. In our data it can be seen how using more then one model replica greatly improved sensitivity and efficiency, with a performance stabilization after 10 replicas (Suppl. Mat. S2); since the number of model replicas greatly impacted computation times we decided to use ten replicas since it was also associated with the higher sensitivity in the same performance cluster. The variability between models derives only from the randomness in the MCMC fitting phase []; an alternative was to impose additional variability by bootstrapping [] but this approach actually decreased performance (Suppl. Mat. S2), probably due to the low proportion of positive matches in the data and the loss of information with bootstrapping in unbalanced classification tasks [].\
The strong imbalance between relevant and non-relevant records [@sampson2011precision] can affect sensitivity []. To overcome the problem, we oversampled the positive records ten times before model fitting. Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance. An alternative approach would be record weighting to change error costs during estimation [] but the BART implementation we used did not allow observation weighting and using simple oversampling allows to use different modeling engines. Also, the simple query ordering of the record during the creation of the initial training set allowed to have a far higher prevalence of relevant records (17.2%) compared to the overall one (0.11%) and this boosts the overall sensitivity of the model. A known risk with oversampling of the target class is the missclassification of negative records as positive [], but since in our approach all predicted positive are manually reviewed we are ensured to achieve always 100% specificity/positive predictive value.\
One of the innovation in our approach is the overcoming of simple stopping rules in SRA classification tasks []. Static supervised learning models requires to manually label a certain amount of records (i.e., the training set) which are then used to train the algorithm and classify the rest (the test set) [], but this method requires to decide the size of the training set in advance. Active learning tries to alleviate the problem by splitting the classification task in an iterative process in which prediction and review phases alternate, but even in this case, one has to define a stopping rule regarding how many records to screen manually in every iteration []. By exploiting the Bayesian nature of BART we produce a distribution of probabilities and not a single value for each record; by joining these distribution in the positive and negative record groups it's possible to identify a "uncertainty zone" so that all record whose predictive distribution crosses this zone needs manual verification. Therefore the researcher will have a defined number or records to check at every iteration which dynamically decreases as uncertain predictions are reviewed and the uncertainty shrinks (Suppl. Mat. S2 Fig. 1). In this model, researcher do not need to choose a priori the number of records to review but just the size of the uncertainty zone (by setting the PPD quantiles used to built it) and after how many iterations with no new positive matches to stop; both the parameters are more theoretical and general than a simple stopping rule and nevertheless the hyperparameter tuning did not indicate a big impact of these parameters. Since our approach requires researchers to review both unlabelled records with a positive predicted label and those with a PPD inside the uncertainty zone, it can be considered as a unifying syinthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

To evaluate performance we avoided the classic random out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study] because we deemed them not realistic in this setting. It is assumed that the corpus to be screened is not a random sample, but the entire population of citation for a given query; a random validation would be useful to estimate the performance of this method on a new dataset derived by the same data-generating process, but this is a totally theoretical goal with no usefulness since all the existing data related was alread acquired. Instead a more relevant question is to estimate the long run sensitivity of our prediction method in finding all relevant records in the whole data set. Since the records are ordered, again a random approach would not work since it assumes that the prevalence of positive records is equal on average in every possible sample [@tashman2000out], while instead it drops as more records are considered (Fig. 2). We instead used a Bayesian model to estimate the likelihood of a positive match given the prediction scores of the BART model. This approach showed to fit the data very well (high $R^2$) and the Bayesian predictive distribution can be exploited to draw a worse case scenario given the data.\
In our study our approach reached 98.8% sensitivity during the hyperparameter optimization (deterministic, small sample ) and on the whole data set we predicted a theoretical sensitivity of 100% [93.5%, 100%] in the first session and of 97.3% [73.8%, 100%] in the second, a lower value as is expected by the probabilistic accumulation of random events; both results are above the usual results in the field [@o2015using] and in line with the 92% average sensitivity estimated after human only screening [@edwards2002identification]. In one interesting case, the model spotted a missclassification during initial labeling, demonstrating its robustness and its value also as a second screener, as already suggested by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].\
Also we showed that such sensitivity was achieved screening just 1.34% of all downloaded records, a sensible reduction in workload; finally, albeit the simple query based ordering did concentrate most of the relevant matches in the first 20-25 thousands records, some relevant records would have required almost the full data set to be manually checked to be found.\
The model takes ~5-20 minutes per iteration to perform predictions in session 1 (17755 documents) and 20-40 minutes in session 2 (98371 documents) on a 8 core, 2.5 GhZ, 16 GB RAM laptop from 2014 and that equate to 1-3 days per session to manually review and perform predictions, for a total of 1-2 weeks for the whole process, a huge saving of time compared to the months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating]. To our knowledge, our data sets are larger than what common in most SRA studies [@o2015using; @olorisade2016critical], emphasizing the reliability of the tool in real world scenarios.\

The last component of our framework is a data-driven query generation algorithm. The creation of an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximize the number of relevant search results while minimizing the total number of results. We propose a solution based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the posterior predicted probabilities; the technique tries to extract high sensitivity subqueries from the labeled data, enrich them with negative terms to increase specificity [@abdelmgeid2008using] and then let researcher evaluate them and pick the most meaningful ones. The framework will then join them and remove redundancies. The aim is to generate a second query that complement the first human made one and help find possible missing records not found during the first session.\
The generated query allowed to retrieve few more positive matches not found in session 1 at the cost of a large increase in the amount of documents. One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules internalized by the classification model, showing which combination of terms was particularly relevant and even spotting authors and locations associated to the topic of study. The generated query therefore acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to spot bias in black box classification algorithms [@malhi2020explainable] and that is increasingly legally required for high-stack machine learning applications [@bibal2021legal; @bibal2020impact].\^
It is important to note that this process is entirely data-driven. The algorithm is only aware of the "world" defined by the data set, itself generated by a specific search query focused on a particular topic. Therefore, the new query may not be specific once applied to an unbounded search domain, returning an unmanageable amount of unrelated results. The solution we found was to add another component specifying the general topic (antimicrobial resistance and healthcare associated infections) of our research.\

As reported, our framwork builds on modularity. We designed it in order to easily implement complete independency of the main modules in future iterations; especially, we plan to allow users create their custom made components in addition or in place of the original ones, further expanding its functionalities. In our view it would be possible to easily add custom citation search and parsing functions for other scientific databases, alternative text features building algorithms and alternative machine learning modules.\
We deem such interoperability extremely relevant, because the main strength of our tool is the composition of many solutions and the general approach related to Bayesian active machine learning, but each of its components could benefit greatly from the recent improvements in text mining.\
For example, our text feature generation approach is based on the boolean bag-of-words paradigm, and surely it could be improved by more nuanced text representations: it could be evaluated if feature transformations like Tf-Idf [@baeza1999modern; @ananiadou2006text], would be advantageous, even if we hypothesize that tree based classification algorithms like BART are robust enough to not need such operation. Word embedding could be considered, which transform terms in semantic vectors based on the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep], and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context; another option would be to use unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis, etc., [@pavlinek2017text; @chen2016short; @landauer1998introduction] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method which produces full PPDs; therefore alternative models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian]. Even more interesting would be to test  advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher level features in the text like term context and sequences, long distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\

>>>>

# Discussion

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.\
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
Our tool consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].

The feature extractor module uses modern NLP techniques [@ananiadou2006text; @cohen2008getting] to transform text into input data for machine learning.
We did not include classical n-grams [@schonlau2017text], but we used network analysis to find non-consecutive frequently associated terms, a generalisation of n-grams relaxing the term adjacency assumption.
A similar network approach was applied to merge redundant terms to make model estimation more efficient and reduce noise.\
The use of concurrency network-driven modelling of text is not new [@rousseau2015graph; @violos2016sentiment; @rousseau2015text; @ohsawa1998keygraph] and is a valuable tool to extract semantic information not evident in one-word or consecutive n-gram models.\

The framework's record classification module implements an active machine learning approach [@settles2009active, @miwa2014reducing] and is based on Bayesian Additive Regression Trees (BART) [@chipman2010bart; @kapelner2013bartmachine].
When implementing our algorithm we adopted best practices from other SRA studies, bringing improvements at various levels.\
As with other boosted trees algorithms [@hastie2009boosting], BART can explore complex non-linearities, perform variable selection, manage missing data while sporting high performance in predictive power.\
However, its Bayesian foundation provides further benefits:
less sensitivity on hyperparameter choices, natural regularisation through priors, and, especially, predictive distributions as output in place of point-wise predictions [@soria2011belm; @joo2020being; @jospin2020hands].
By selecting relatively tight prior distributions, we discouraged excessively deep trees, long sequences of trees, or extreme predicted probabilities, to decrease the risk of overfitting.\
The algorithm runs multiple replications of the model and averages their predictive distributions creating an "ensemble";
this technique has been shown to improve out-of-sample predictive performance [@zhou2021ensemble; @dietterich2000ensemble], as we were able to confirm during the hyperparameter evaluation (Supplemental Material S2).
Ensembling reduces the uncertainty in the predictive distribution tails related to the randomness in the MCMC fit [@robert2004monte], generating a shift of probability mass towards the distribution centre and stabilising it (i.e., decreasing variance without impacting bias).
On the other hand, just imposing robust uninformative priors against extreme predictions would have decreased variance but also shifted the distribution towards a non-decision zone, increasing bias [@hansen2000bayesian].\
Since the number of model replications significantly impacts computation times, we decided to use ten replicas, the lower value after which showed performance stabilisation during the hyperparameter evaluation.\
We also investigated whether bootstrapping between replications [@breiman1996bagging] would improve performance, but, contrary to theory [@diez2015diversity], it was demonstrated to be slightly detrimental (Supplemental Material S2) compared to simple ensembling.\

A low rate of relevant matches (class imbalance) is typical in literature reviews [@sampson2011precision; @wallace2010semi; @o2015using], and such strong imbalance between positive and negative records can affect sensitivity [@khoshgoftaar2010comparing; @chawla2004special].\
To overcome the problem, we oversampled [@batista2004study] the positive records ten times before model fitting.
Our hyperparameter analysis showed that together with model ensembling, the oversampling rate was the parameter with the highest impact on performance.\
A known risk with positive oversampling is the misclassification of negative records [@ramezankhani2016impact].
However, since all predicted positives get manually reviewed in our approach, we are always ensured to achieve 100% specificity/positive predictive value: the only price for the increased sensitivity due to oversampling is a larger number of records to review.\
An alternative to oversampling would be applying different weights and/or cost to the classes [@abd2013review; @diez2015diversity], but the BART implementation we used did not have this feature;
also, using simple oversampling permits broader compatibility with different modelling engines [@galar2011review; @roshan2020improvement].\
Finally, ordering the records by query term frequency (simple query ordering) generates a far higher rate of relevant records in the initial training set (17.2%) compared to the overall data (0.11%), and this boosts the sensitivity of the model.\

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

We evaluated performance as the capability of the screening procedure (automatic classification plus manual review) to find the largest number of relevant records while reviewing as few of them as possible (i.e., sensitivity $\times$ efficiency).\
We avoided the classic out-of-sample approaches like train-test sampling, out-of-bag bootstrapping or cross-validation [@kohavi1995study; @james2013introduction].
Such methods primarily assume that the rate of positivity is equal on average in every random subset of the data [@tashman2000out];
this uniformity is broken by how the initial training set and the subsequent reviewed records are selected by the query-based ordering and the active learning algorithm, determining a lower positivity rate in the unlabelled records (Fig. 2).
Also, a literature corpus is unique per search query/database combination, and therefore any out-of-sample performance estimate is not replicable since no new data can be acquired related to the current corpus.\
Instead, to estimate overall sensitivity, we employed simple Bayesian regression (surrogate model) on the manually reviewed data to abstract the classification model predictions and achieve a maximum entropy [@harremoes2001maximum] estimate of the number of missed positive matches among the unreviewed records in the whole dataset.
This simple surrogate model fitted the data very well ($R^2$ consistently above 97%) using just the lower 98% PrI bound of the PPDs as predictor, indicating predictive consistency in the classification model.
The surrogate model posterior predictive distribution could be exploited to explore worse case scenarios in terms of sensitivity.\

Our framework achieved very high sensitivity by screening a markedly small fraction of all records, bringing a sensible reduction in workload.\
Based on the surrogate model, we predicted a predicted median sensitivity of 100% [93.5%, 100%] in the first session (screening 4.29% of records) and of 97.3% [73.8%, 100%] in the second (screening 1.34% of records):
efficiency increased significantly in the second session since only a few new positive matches were found, but given the large number of records, uncertainty regarding sensitivity also expectedly increased.\
Both results are above the usual performance in the field [@o2015using] and in line with the 92% average sensitivity estimated after human-only screening [@edwards2002identification].
In one interesting case, the model spotted a human-made misclassification error, demonstrating its robustness and value as a second screener, a role already suggested for SRA tools by previous studies [@frunza2010building; @bekhuis2012screening; @bekhuis2010towards].
Finally, albeit the simple query ordering already concentrated most of the relevant matches in the first 20-25 thousand records, without the tool support some relevant records would have required almost the complete data set to be manually checked to be found.\

The model took ~5-20 minutes per iteration to perform predictions in session 1 (17,755 documents) and 20-40 minutes in session 2 (98,371 documents) on an eight-core, 2.5 GHz, 16 GB RAM laptop from 2014;
including manual record review, one session required 1-3 days of work, for a total of 1-2 weeks for the whole process (including record collection).
That is a considerable saving of time compared to the multiple months usually required for the screening phase of systematic reviews [@bannach2019machine; @borah2017analysis; @allen1999estimating].
To our knowledge, the amount of data processed (~100.000 records) were larger than what is typical in most SRA studies [@o2015using; @olorisade2016critical], emphasising the reliability of the tool in real-world scenarios.\

The last module of our framework is a data-driven query generation algorithm.
Creating an efficient and efficacious search query is a complex task [@lefebvre2011searching; @hammerstrom2010searching] since it requires building a combination of positive and negative terms to maximise the number of relevant search results while minimising the total number of records to review.
Our solution joins a sensitivity-driven subquery proposal engine based on concurrent decision trees [@blanco2019machine; @moore2018transparent] built on the BART ensemble PPD with a human review step and an efficiency-driven query builder.
The aim is to generate a second query that helps find records missed during the first session search.
The generated query allowed indeed to retrieve few more positive matches not found in session 1, but at the cost of a significant increase in the number of documents.\
One interesting aspect of this functionality is that it provides a human-readable overview of the classification rules learned by the classification model, showing which combination of terms was particularly relevant and even spotting authors and geographical locations associated with the study topic.
The generated query, therefore, acted as a tool for machine learning explainability [@bhatt2020machine; @burkart2021survey], a feature useful to understand and spot bias in black-box classification algorithms [@malhi2020explainable];
explainability is often required or even legally mandatory for high-stake machine learning applications [@bibal2021legal; @bibal2020impact].\
It is important to note that this process is entirely data-driven.
The algorithm is only aware of the "world" defined by the data set used as input, which is generated by a specific search query focused on a particular topic.
Therefore, the new query may not be specific enough once applied to an unbounded search domain, returning an unmanageable amount of unrelated results.
The solution we found was to add another component to the query, specifying the general topic (antimicrobial resistance and healthcare-associated infections) of our research.\

As reported, our framework builds on modularity.
We designed it to easily implement complete independence of the main modules in future iterations, making it possible for users to add custom features like citation search and parsing for other scientific databases, alternative text processing algorithms or machine learning modules.
We deem such interoperability extremely relevant because the main strength of our tool is the composition of many solutions and the general idea of Bayesian active machine learning and uncertainty zone.
However, each of its components could benefit considerably from the recent improvements in text mining.\
For example, our text processing approach is quite simple, based on the boolean bag-of-words paradigm, and indeed could be improved by more nuanced text representations.
It could be evaluated if feature transformations like TF-IDF [@baeza1999modern; @ananiadou2006text] would be advantageous, even if we hypothesise that tree-based classification algorithms like BART are robust enough not to need such operations.
Word embedding could be worth exploring:
this technique transforms terms in semantic vectors derived from the surrounding text [@turian2010word; @bollegala2015embedding, @minaee2021deep] and could be used to eliminate semantically redundant terms or differentiate identical terms with different meanings given the context.
Another option would be to employ unsupervised learning models like Latent Dirichlet Analysis, Latent Semantic Analysis [@pavlinek2017text; @chen2016short; @landauer1998introduction] or graph-of-word techniques [@ohsawa1998keygraph; @rousseau2015graph] to extract topics to enrich the feature space.\
Our classification algorithm can be implemented with any Bayesian supervised machine learning method that provides full PPDs;
therefore alternative classification models could be evaluated, like Gaussian Processes which are known for their flexibility [@jayashree2020evaluation; @chen2015gaussian].
Even more interesting would be to test advanced learning algorithms that surpass the bag-of-words approach, taking into consideration higher-level features in the text like term context and sequences, long-distance term relationships, semantic structures, etc., [@cheng2019document; @minaee2021deep; @li2020survey; @yang2020survey; @lai2015recurrent; @farkas1995document], given that a Bayesian implementation of such algorithms is available (for example @chen2018approximate).\
Finally, a natural improvement would be to provide a graphical user interface to make the framework easy to use also for less technical users.

The field of literature review automatisation is mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.
The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of solutions we developed to solve various SRA issues and that can be used to improve existing solutions.

### 2021-10-25 Manuscript/Manuscript_Results.Rmd
update

```{r load framework, cache.rebuild=TRUE}
source(file.path('R', 'Setup.R'))

@@

## Results

@@

### First session

@@

### Second session

@@

### Hyperparameter selection

@@

### Performance evaluation

@@

`r print_table(perf_table, caption = "**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, *Sensitivity* and *Work saved over random* (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian R^2 [90% CrI] of the logistic models is reported. [PrI] represents the 90% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).")`

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="Figure 2. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

>>>>

```{r load framework, cache.rebuild=TRUE, include=FALSE}
source(file.path('R', 'Setup.R'), local = knitr::knit_global())

@@

# Results

@@

## First session

@@

## Second session

@@

## Hyperparameter selection

@@

## Performance evaluation

@@

`r print_table(perf_table, caption = '**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported. [PrI] represents the 90% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).')`

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}
